Reconstructing the last known movements of one of Nature's giants

### 2018-11-02 manuscript/PRSB/blue-new-supplementary.tex
Add PRSB version

% Preamble
\documentclass[a4paper,10pt]{article}

%\usepackage[osf]{mathpazo} % palatino
%\usepackage{ms1}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{parskip} 
\usepackage{amsmath}
\usepackage{textcomp} % for parts per mille symbol  
\usepackage{pdflscape} % landscape   
\pagenumbering{arabic}

% Weird Current Biology rules about times and single line spacing
\linespread{1}
\usepackage{times}

@@

\section*{Supplemental Results: Pacific blue whales from Busquets-Vass et al. 2017}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top25.moveWhaleA_TL2.eps}
      \caption{Simulated locations by month taken from the top 25\% best fitting migratory movement model simulations for Pacific blue whale A.}
      \label{figwhaleA}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top25.moveWhaleB_TL2.eps}
      \caption{Simulated locations by month taken from the top 25\% best fitting migratory movement model simulations for Pacific blue whale B.}
      \label{figwhaleB}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top25.moveWhaleC_TL2.eps}
      \caption{Simulated locations by month taken from the top 25\% best fitting migratory movement model simulations for Pacific blue whale C.}
      \label{figwhaleC}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top25.moveWhaleD_TL2.eps}
      \caption{Simulated locations by month taken from the top 25\% best fitting migratory movement model simulations for Pacific blue whale D.}
      \label{figwhaleD}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top10.moveWhaleE_TL2.eps}
      \caption{Simulated locations by month taken from the top 10\% best fitting migratory movement model simulations for Pacific blue whale E.}
      \label{figwhaleE}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/top25.moveWhaleF_TL2.eps}
      \caption{Simulated locations by month taken from the top 25\% best fitting migratory movement model simulations for Pacific blue whale F.}
      \label{figwhaleF}
  \end{figure}
\end{landscape}

>>>>

% Preamble
\documentclass[a4paper,10pt]{article}
\usepackage[margin = 2cm]{geometry}
\usepackage[osf]{mathpazo} % palatino
%\usepackage{ms1}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{parskip} 
\usepackage{amsmath}
\usepackage{textcomp} % for parts per mille symbol  
\usepackage{pdflscape} % landscape   
\usepackage[multidot]{grffile} % deal with weird image issue where it can't cope if names have "." in them

\pagenumbering{arabic}

@@

\newpage
\section*{Supplemental Results: Pacific blue whales from Busquets-Vass et al. 2017}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[angle = 90, origin = c, scale = 0.65]{figures/top25.moveWhaleA_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale A. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleA}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth, scale = 0.55]{figures/top25.moveWhaleB_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale B. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleB}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[angle = 90, origin = c, scale = 0.65]{figures/top25.moveWhaleC_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale C. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleC}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[angle = 90, origin = c, scale = 0.65]{figures/top25.moveWhaleD_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale D. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleD}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[angle = 90, origin = c, scale = 0.65]{figures/top10.moveWhaleE_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale E. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleE}
  \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!htbp]
    \centering
      \includegraphics[angle = 90, origin = c, scale = 0.65]{figures/top25.moveWhaleF_TL2.pdf}
      \caption{Locations corresponding to the top 25\% best-fitting migratory movement model simulations for Pacific blue whale F. Data from Busquets-Vass et al. 2017.}
      \label{figwhaleF}
  \end{figure}
\end{landscape}

### 2018-11-02 manuscript/PRSB/blue-new.tex
Add PRSB version

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{textcomp} % for parts per mille symbol     
\pagenumbering{arabic}    
\linespread{1.66}

@@

\section{Abstract} % 150 words only

@@

\section{Main text}\label{background}

@@

%\subsection{Data Code and Materials}\label{data-code-and-materials}
\subsection{Data Availability}
Data are available from the NHM Data Portal (https://doi.org/10.5519/0093278). 
R code is available from GitHub (https://github.com/nhcooper123/blue-whale-bes)(Zenodo DOI will be added before publication).

@@

@@

\section{Competing interests}
The authors declare no competing interests.

>>>>

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
%\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{textcomp} % for parts per mille symbol     
\pagenumbering{arabic}    
\linespread{1.66}

@@

\section{Abstract} % 200 words only

@@

\textbf{Keywords: carbon stable isotopes, movement models}

\section{Background}\label{background}

@@

@@

\section{Competing interests}
We have no competing interests.

@@

\subsection{Data Code and Materials}\label{data-code-and-materials}
Data are available from the NHM Data Portal (https://doi.org/10.5519/0093278). 
R code is available from GitHub (https://github.com/nhcooper123/blue-whale-bes)(Zenodo DOI will be added before publication).
